---
title: "Using simulation determin barcode threshold"
author: "Wenjie Sun"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
    number_sections: yes
    theme: united 
    fig_caption: true
    highlight: textmate
    keep_md: false 
always_allow_html: yes
---

```{r echo=F}
library(knitr)
opts_chunk$set(echo=T, TOC=T)
```

# About

Here we show how to use the simulation tool to help determine the threshold to filtering barcode.

Because the simulation tool needs several parameters, for rigorious purpose, we suggest to have a conservative estimation.

# Simulate data

## Load Package

```{r}
library(CellBarcodeSim)
library(CellBarcode)
```

## Simulate barcode sequencing data

```{r}
barcode_library = system.file("data", "random_barcodes.tsv", package = "CellBarcodeSim")

## Simulate a barcode sequencing experiment
simulate_main(
    barcode_library_file = barcode_library,  ## Define the barcode library
    clone_n              = 20,  ## Define the number of clones
    clone_size_dist      = "uniform", ## Define the clone size distribution
    clone_size_dist_par  = list(size_max = 1000, size_min = 1),  ## Define the parameters of the clone size distribution
    cycle                = 30,  ## Define the number of PCR cycles
    efficiency           = 0.705, ## Define the efficiency of the PCR cycle
    error                = 1e-6,  ## Define the error rate of the PCR, mutation per base per cycle
    pcr_read_per_cell    = 50,  ## Define the number of PCR reads per cell (clone_n)
    output_prefix        = "./tmp/simu_seq",  ## Define the output prefix
    ngs_profile          = "MSv1",  ## Define the NGS profile (refer to ART sequencing simulator manual)
    reads_length         = 35,  ## Define the length of the reads
    top_seq              = "AAAAAAAAAAGGGGG",  ## Define the fixed sequence at the 5' end of the reads to be added
    bottom_seq           = "TTTTTTTTTT",  ## Define the fixed sequence at the 3' end of the reads to be added
    sequence_trunk       = 10, ## Define the length of the fixed sequence to be added
    art_bin              = NULL ## Define the path to the ART sequencing simulator
)
```

Load the true barcode sequence

```{r}
## Load the true barcode sequence
barcode_true = fread("./tmp/simu_seq_ref.tsv")
head(barcode_true)
```

Load the simulated barcode sequencing data

```{r}
fq = "./tmp/simu_seq.fq"
```

# Test threshold

Here we tried to read in the simulated barcode sequencing result and try to show how the threshold works.

We draw sequence frequency count distribution and labled the true barcode by red fragment underneith.
The automatic threshold is calculated by `bc_auto_cutoff` function, and shown by the red vertical line.

The result shows that the automatic threshold can keep most of the true barcode, and filter out the false barcode.

```{r}
## Extract barcode 
bc = bc_extract(fq, pattern = "AAAAAAAAAAGGGGG(.{10})TTTTTTTTTT")

## Apply the bc_cure_depth with actully no filtering, 
## in order to make possible to plot the frequency distribution
bc = bc_cure_depth(bc, depth = 0)

## Try using automatic threshold
auto_threshold = bc_auto_cutoff(bc)

## Plot the sequence frequency distribution filtering
bc_plot_single(bc, count_marks = auto_threshold, highlight = barcode_true$seq)
```


